Perceptual symbol grounding in \\holographic memories

### 2016-11-07 papers/hrr-paper/paper.tex
Switch bibliography back end to biber

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

@@

\usepackage{cite}

@@

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{Implicit Holographic Memories}

@@

	Vector Symbolic Architectures (VSA) define a set of operations for storage (compression) and retrieval of symbolic concepts in fixed size vectors. As described in \cite{vsa1}, every VSA has to implement three basic operations:
	\begin{enumerate}
		\item association (binding) $\mapsto \otimes$
		\item superposition (appending) $\mapsto +$
		\item probing (unbinding) $\mapsto \oslash$
	\end{enumerate}

@@

	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{hrr-1}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{bsc-1}, Holographic Graph Neurons\cite{holographic-graph-nouron}, Geometric Algebras\cite{geometric-algebra} and Random Permutations. The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}. Authors in \cite{learning-language} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs. Some of the other work is centered around pattern recognition \cite{pattern-recognition}, functional large-scale cognitive architecture models \cite{spaun} and representing scene structure \cite{scene-structure}. Some preliminary theoretical assumptions have been made about ability to use them as agent controllers\cite{embedding-behaviour}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.

@@

	\include{bibliography}

>>>>

% *** CITATION PACKAGES ***
%
%% Use biber instead of BibTeX
%\usepackage[citestyle=numeric,style=numeric,backend=biber]{biblatex}
\usepackage[
	hyperref=true,
	url=false,
	isbn=false,
	citestyle=alphabetic,
	style=alphabetic,
	maxcitenames=3,
	maxbibnames=100,
	backref=true,
	backend=biber
]{biblatex}
\usepackage[babel,german=quotes,english=american]{csquotes}

%TODO check 
%\appto{\bibsetup}{\raggedright}
\appto{\bibsetup}{\sloppy}
\addbibresource{paper.bib}

%\DefineBibliographyStrings{english}{%
%    backrefpage  = {see p.}, % for single page number
%    backrefpages = {see pp.} % for multiple page numbers
%}

@@

@@

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{Perceptual symbol grounding in \\holographic memories}

@@

	Vector Symbolic Architectures (VSA) define a set of operations for storage (compression) and retrieval of symbolic concepts in fixed size vectors. As described in \cite{Levy:2008:VectorSymbolicArchitectures}, every VSA has to implement three basic operations:
	\begin{enumerate}
		\item association (binding) $\mapsto \otimes$
		\item superposition (appending) $\mapsto +$
		\item probing (unbinding) $\mapsto \oslash$
	\end{enumerate}

@@

	Depending of the way these three operations are implemented we can distinguish several popular VSAs, such as Holographic Reduced Representations \cite{hrr-1}, Circular HRRs \cite{circular-hrr}, Binary Spatter Codes \cite{bsc-1}, Holographic Graph Neurons\cite{Kleyko:2016:HolographicGraphNeuron}, Geometric Algebras\cite{Patyk-Lonska:2011:DistributedRepresentationsBased} and Random Permutations. The most widely used ones are HRRs and they are briefly explained in section \ref{sec:hrr}. Authors in \cite{learning-language} have used them to solve word embedding problem for extremely large dataset by replacing computationally expensive big matrix factorization with iterative estimation algorithm based on HRRs. Some of the other work is centered around pattern recognition \cite{Kleyko:2016:PatternRecognitionVector}, functional large-scale cognitive architecture models \cite{spaun} and representing scene structure \cite{scene-structure}. Some preliminary theoretical assumptions have been made about ability to use them as agent controllers\cite{embedding-behaviour}, where a symbolic program is represented with a set of combined symbolic actions associated with actuator symbols and symbolic sensing.

	\begin{figure}
		\center
		\includegraphics[width=0.9\columnwidth]{img/cover_photo.png}
		\caption{In-memory representation of top-down attention shift for visual scene short-term  memory}
	\end{figure}

@@

	%% Add entry to the table of contents for the bibliography
	\printbibliography[heading=bibintoc]
